---
title: "TestFundReport"
author: "RobHayward"
date: "16 September 2017"
output: 
  html_document: 
    fig_width: 10
    theme: journal
    df_print: paged
---
##this is the fund report for xxx
This week was a difficult time for financial markets.  The on-going tension with North Korea and the concern about US interest rates were offset by a more accomodative positon in Washington. 

###Your portfolio 

```{r, echo=FALSE, results='asis', warning=FALSE}
require(xtable)
b <- portfolio[['td126']]
b[,1] <- as.character(a[,1])
colnames(b) <- c("Date", "Cash Holding", "Equity Holding", 
                   "Debt Holding") 
print(xtable(b), type='html', include.rownames = FALSE) 
```
##Transactions

The transactions that have been carried out are recorded as follows. 

```{r, echo=FALSE, results='asis', warning=FALSE}
c <- transactions[['td126']]
c[,1] <- as.character(c[, 1])
colnames(c) <- c("Date", "Buy or Sell", "Asset", "Volume", "Price", "Total")
print(xtable(c), type='html', include.rownames=FALSE)
```
      
The main events in the week ahead are: 

* The ECB meeting on Thursday

* US Employment data on Friday. 

* The debate in the EU over Brexit

* The on-going situation in Asia with fuether talks on the NK missile. 

See (The linl)[https://www.ft.com/week-ahead]

=========================

```{r, echo=FALSE}
barplot(a[,7], main = "Portfolio Value", names.arg = a[,1])
```